---
title: "BMW Used Car Market Dashboard"
author: "Zifan Ye"
date: "`r Sys.Date()`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme: cosmo
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(DT)
library(readr)
library(dplyr)
library(scales)
library(htmltools)

bmw <- read_csv("/Users/ye.fun/Desktop/QQQ/bmw.csv", show_col_types = FALSE)

bmw_clean <- bmw %>%
  rename(
    fuel_type = fuelType,
    engine_size = engineSize
  ) %>%
  mutate(
    tooltip_scatter = paste0(
      "Model: ", model,
      "<br>Year: ", year,
      "<br>Price: £", comma(price),
      "<br>Mileage: ", comma(mileage), " miles",
      "<br>Fuel type: ", fuel_type
    ),
    tooltip_box = paste0(
      "Fuel type: ", fuel_type,
      "<br>Price: £", comma(price),
      "<br>Year: ", year,
      "<br>Mileage: ", comma(mileage), " miles"
    )
  ) %>%
  filter(!is.na(price), !is.na(mileage), !is.na(fuel_type))

```
Overview
=====================================

Row
-------------------------------------
BMW Resale Price vs Mileage  

```{r cars}
plot_ly(
  data = bmw_clean,
  x = ~mileage,
  y = ~price,
  type = "scatter",
  mode = "markers",
  color = ~fuel_type,
  text = ~tooltip_scatter,
  hoverinfo = "text",
  marker = list(size = 7, opacity = 0.7)
) %>%
  layout(
    title = list(text = "BMW Resale Price vs Mileage"),
    xaxis = list(title = "Mileage (miles)"),
    yaxis = list(title = "Resale Price (£)"),
    legend = list(title = list(text = "Fuel Type"))
  )
```
Row
-------------------------------------
The main pattern is easy to see: BMW resale prices generally decrease as mileage increases.  
This chart also lets users compare fuel types and inspect individual cars through hover tooltips.  

Row
-------------------------------------
##BMW Price Distribution by Fuel Type  
```{r}
plot_ly(
  data = bmw_clean,
  x = ~fuel_type,
  y = ~price,
  type = "box",
  color = ~fuel_type,
  text = ~tooltip_box,
  hoverinfo = "text",
  boxpoints = "all",
  jitter = 0.25,
  pointpos = 0
) %>%
  layout(
    title = list(text = "BMW Price Distribution by Fuel Type"),
    xaxis = list(title = "Fuel Type"),
    yaxis = list(title = "Resale Price (£)"),
    showlegend = FALSE
  )
```
Row
-------------------------------------
This chart shows how price varies across fuel types, including differences in spread and outliers.  
It helps users move from the overall trend to a more detailed group comparison.

Row
-------------------------------------
##Explore the BMW ListingsRow  
```{r}
datatable(
  bmw_clean %>%
    select(model, year, price, mileage, fuel_type, transmission, mpg, engine_size),
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 8,
    autoWidth = TRUE,
    scrollX = TRUE
  ),
  colnames = c(
    "Model",
    "Year",
    "Price (£)",
    "Mileage (miles)",
    "Fuel Type",
    "Transmission",
    "MPG",
    "Engine Size (L)"
  )
)
```
Dataset Description
=====================================
Row
-------------------------------------
The dataset comes from the Kaggle dataset Used Car Dataset: Ford and Mercedes, which includes a BMW file (bmw.csv).  
This dashboard uses the BMW subset only, with each row representing one used BMW listing.  
The data were collected from used-car listings and compiled into a structured CSV dataset for analysis.  
The study population is BMW vehicles in the used car market, and the sample size is the number of rows in bmw.csv.  
Source: https://www.kaggle.com/datasets/adityadesai13/used-car-dataset-ford-and-mercedes

Repository
=====================================
Row
-------------------------------------
###GitHub Repository  

 https://github.com/yourusername/bmw-dashboard(改)  
#Why this project matters  
This project matters because used-car buyers often need simple tools to compare price patterns across many listings.  
The dashboard makes those patterns easier to understand and supports more informed purchasing decisions.  