---
title: "BMW Used Car Market Dashboard"
author: "Zifan Ye"
date: "`r Sys.Date()`"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: cosmo
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(DT)
library(readr)
library(dplyr)
library(scales)
library(htmltools)

bmw <- read_csv("/Users/ye.fun/Desktop/QQQ/bmw.csv", show_col_types = FALSE)

bmw_clean <- bmw %>%
  rename(
    fuel_type = fuelType,
    engine_size = engineSize
  ) %>%
  mutate(
    tooltip_scatter = paste0(
      "Model: ", model,
      "<br>Year: ", year,
      "<br>Price: £", comma(price),
      "<br>Mileage: ", comma(mileage), " miles",
      "<br>Fuel type: ", fuel_type
    ),
    tooltip_box = paste0(
      "Fuel type: ", fuel_type,
      "<br>Price: £", comma(price),
      "<br>Year: ", year,
      "<br>Mileage: ", comma(mileage), " miles"
    )
  ) %>%
  filter(!is.na(price), !is.na(mileage), !is.na(fuel_type))

```
Overview
=====================================

Row {data-height=650}
-------------------------------------

### BMW Resale Price vs Mileage

```{r cars, echo=FALSE}
plot_ly(
  data = bmw_clean,
  x = ~mileage,
  y = ~price,
  type = "scatter",
  mode = "markers",
  color = ~fuel_type,
  text = ~tooltip_scatter,
  hoverinfo = "text",
  marker = list(size = 7, opacity = 0.7)
) %>%
  layout(
    title = list(text = "BMW Resale Price vs Mileage"),
    xaxis = list(title = "Mileage (miles)"),
    yaxis = list(title = "Resale Price (£)"),
    legend = list(title = list(text = "Fuel Type")),
    height = 450,
    margin = list(b = 0)
  )
```

### Take away 1  

BMW resale prices generally decrease as mileage increases, showing a clear negative relationship between vehicle use and resale value.
The highest-priced vehicles are concentrated at lower mileage levels, while lower-priced cars become much more common as mileage rises.
The hover tooltips also help users inspect specific listings in greater detail.

Row {data-height=650}
-------------------------------------
### BMW Price Distribution by Fuel Type

```{r boxplot, echo=FALSE}
plot_ly(
  data = bmw_clean,
  x = ~fuel_type,
  y = ~price,
  type = "box",
  color = ~fuel_type,
  text = ~tooltip_box,
  hoverinfo = "text",
  boxpoints = "all",
  jitter = 0.25,
  pointpos = 0
) %>%
  layout(
    title = list(text = "BMW Price Distribution by Fuel Type"),
    xaxis = list(title = "Fuel Type"),
    yaxis = list(title = "Resale Price (£)"),
    showlegend = FALSE,
    height = 450,
    margin = list(b = 0)
  )
```

### Take away 2 

The boxplot shows that resale price distributions differ by fuel type, both in median price and in overall variability.  
Some fuel categories have narrower interquartile ranges, while others have wider spreads and more visible outliers, suggesting more variation within those groups.  
The plotted individual points help users connect the summary boxes to the listing-level prices shown in the data.  

Row
-------------------------------------
### Explore the BMW ListingsRow  

```{r}
datatable(
  bmw_clean %>%
    select(model, year, price, mileage, fuel_type, transmission, mpg, engine_size),
  rownames = FALSE,
  filter = "top",
  options = list(
    pageLength = 8,
    autoWidth = TRUE,
    scrollX = TRUE
  ),
  colnames = c(
    "Model",
    "Year",
    "Price (£)",
    "Mileage (miles)",
    "Fuel Type",
    "Transmission",
    "MPG",
    "Engine Size (L)"
  )
)
```
Dataset Description
=====================================
Row
-------------------------------------
The dataset comes from the Kaggle dataset *100,000 UK Used Car Data set*, and this dashboard analyzes the BMW subset (`bmw.csv`).  
The study population is used BMW vehicles listed in the UK market, and the sample size is the number of records in `bmw.csv`.
Each observation represents one used BMW listing, with variables such as model, year, price, mileage, fuel type, transmission, MPG, and engine size.  
The data were collected from UK used-car listings around the year 2020 and organized into a structured CSV file for analysis.   
Source: <https://www.kaggle.com/datasets/adityadesai13/used-car-dataset-ford-and-mercedes>

Repository
=====================================
Row
-------------------------------------
### GitHub Repository  

https://github.com/yezifan911-hash/bmw-dashboard 

### Why this project matters  
This project matters because used-car buyers often need simple tools to compare price patterns across many listings.  
The dashboard makes those patterns easier to understand and supports more informed purchasing decisions.  